---
title: "Week 3: plotly homework assignment"
author: "Magnus Ahlström"
date: "3 aug 2018"
output: ioslides_presentation
---

```{r setup, include=F}
knitr::opts_chunk$set(message = F, warning = F, cache=F)
```

##Best prediction of miles pr gallon based on the mtcars dataset

- In the following slides I will try to evaluate what kind relationship that best fits the association between weight and miles pr. gallon in the mtcars dataset.

- I will fit three univariate linear regression models with the miles pr. gallon as the response and the weight, weight squared and log weight as the predictors

- I will then try to evaluate which one gives the best prediction based on a grphical evaluation and based on the

##Code to produce the modify the data and fit the models
```{r}
##A function to calculate the mean squared error
mse <- function(fit) mean((summary(fit)$residuals)^2)

##Lodaing packages and modifying the mtcars dataset
library(plotly); library(dplyr); library(tidyr)
mtcars_mod <- mtcars %>%
    mutate(log_wt = log(wt),
           squared_wt = wt^2)

#Fitting the models as described above
fit_lin <- lm(mpg ~ wt, data = mtcars_mod)
fit_sq <- lm(mpg ~ squared_wt, data = mtcars_mod)
fit_log <- lm(mpg ~ log_wt, data = mtcars_mod)
```

##A little formatting to the plot
```{r}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "Weight (ton)",
  titlefont = f
)
y <- list(
  title = "Miles pr gallon (km)",
  titlefont = f
)
```
##Code for the plot (Plot is not next slide)
```{r, eval = F}
plot_ly(data = mtcars_mod, x = ~wt, y = ~mpg, 
        type = "scatter", 
        mode = "markers", 
        name = "Observed") %>%
    add_lines(x = ~wt, y = predict(fit_lin), 
              name = "Linear prediction") %>%
    add_lines(x = ~wt, y = predict(fit_sq), 
              name = "Squared prediction") %>%
    add_lines(x = ~wt, y = predict(fit_log), 
              name = "Logarithmic prediction") %>%
    layout(xaxis = x,
           yaxis = y)
```

##The plot
```{r, echo = F}
plot_ly(data = mtcars_mod, x = ~wt, y = ~mpg, 
        type = "scatter", 
        mode = "markers", 
        name = "Observed",
        xaxis = x,
        yaxis = y) %>%
    add_lines(x = ~wt, y = predict(fit_lin), 
              name = "Linear prediction") %>%
    add_lines(x = ~wt, y = predict(fit_sq), 
              name = "Squared prediction") %>%
    add_lines(x = ~wt, y = predict(fit_log), 
              name = "Logarithmic prediction") %>%
    layout(xaxis = x,
           yaxis = y)
```

##Best prediction
From the graph it looks like the best prediction of miles pr. gallon comes from taking the log of weight and making a fit based on that. This is also indicated by the mean squared error which is, `r round(mse(fit_lin), 2)` for the linear prediction, `r round(mse(fit_sq), 2)` for the squared prediction and `r round(mse(fit_log), 2)` for the logarithmic prediction.

##Thanks