---
title: "Academic output of universities"
author: "Magnus Ahlström"
date: "15 aug 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

****

####The basic idea
- <font size="4">To use meta data on articles from the medline database to rank universities based on their academic output.</font>

####Data collection

- <font size="4">Metadata was collected by manually downloading medline files from pubmed and parsing these to R readable lists, read about it [here](https://mlbernauer.wordpress.com/2014/12/15/parsing-medline-files-in-r/).</font>

- <font size="4">From these lists author affiliations were extracted and mined for information on university.</font>

- <font size="4">I then used the geocode function from [ggmap package](http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf) to find coordinates of the universities to be able to display them on a leaflet map.</font>

- <font size="4">Finally I extracted publication date and pubmed-ids to be able to filter proporly and link to articles.</font>
    

##Simplified code example {.smaller}

From medline file to university with coordinates
```{r}
source("medline.R"); require(ggmap); require(dplyr)
med <- medline("medline_file_more_IDs.txt")
out <- lapply(med, function(x) {
  aff <- strsplit(x$AD, ";")[[1]][1]
  P <- if(!is.null(x$LR)) x$LR else "NA" 
  PMID <- x$PMID
  re <- "\\,[[:alpha:][:space:]]*[Uu][Nn][Ii][Vv][[:alpha:][:space:]]*\\,"
  ind <- regexpr(re, aff)
  uni <- sub("^\\,\\ ", "", substr(aff, ind, ind[1] + attributes(ind)[[1]]))
  uni <- sub(", $", "", uni)
  list(Uni = uni, Published = P, PMID = PMID)
})
outdf <- do.call(rbind.data.frame, c(out, stringsAsFactors = F)) %>%
  filter(Uni == "University of Copenhagen") %>%
  mutate(Published = as.Date(Published, format = "%Y%m%d")) %>%
  arrange(desc(Published))
uni <- unique(outdf$Uni)
coords <- data.frame(Uni= uni, geocode(uni, source = "dsk"))
outdf <- left_join(outdf, coords, by = "Uni")
head(outdf, 1)

```

##Continued {.smaller}

Then we do a little more modulation to create the links for the articles
```{r}
require(leaflet)
pubs <- slice(outdf, 1:5) %>% pull(PMID)
as_a_link <- lapply(pubs, function(t) {
  paste("<a href='https://www.ncbi.nlm.nih.gov/pubmed/", 
        t, 
        "'>", 
        t, 
        "</a>", 
        sep = "")
  })
linkdf <- data.frame(Uni = "University of Copenhagen", 
                     link = do.call(paste, c(as_a_link, sep = " <br> ")))
outdf <- left_join(outdf, linkdf, by = "Uni") %>%
  mutate(link = paste0(Uni, 
                       " <br> ",
                       "Publications in medline file ", 
                       nrow(outdf),
                       " <br> ", link))
lf <- leaflet(data = outdf) %>% 
    addTiles() %>%
    addMarkers(lng = ~lon, 
               lat = ~lat, 
               popup = ~link)
```



##Leafletify
Voila !!!
```{r, echo = F}
lf
```
[To see the final result click here](https://magnusdhk.shinyapps.io/Academic_output/)