---
title: "Academic output of universities"
author: "Magnus Ahlström"
date: "15 aug 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r, echo = F}
source("medline.R")
library(ggmap)
```

****

###The basic idea
- To use meta data on articles from the medline database to rank universities based on their academic output.

###Data collection

- Metadata was collected by manually downloading medline files from pubmed and parsing these to R readable lists, read about it [here](https://mlbernauer.wordpress.com/2014/12/15/parsing-medline-files-in-r/).

- From these lists author affiliations were extracted and mined for information on university.

- I then used the geocode function from [ggmap package](http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf) to find coordinates of the universities to be able to display them on a leaflet map. 

- Finally I extracted publication date and pubmed-ids to be able to filter proporly and link to articles.

##Example

```{r, message = F}
med <- medline("medline_file_PMID28657967.txt")[[1]]
aff <- strsplit(med$AD, ";")[[1]][1]
re <- "\\,[[:alpha:][:space:]]*[Uu][Nn][Ii][Vv][[:alpha:][:space:]]*\\,"
ind <- regexpr(re, aff)
uni <- sub("^\\,\\ ", "", substr(aff, ind, ind[1] + attributes(ind)[[1]]))
uni
geocode(uni, source = "dsk")
```
